\documentclass{book}
\usepackage{geometry}
\geometry{a5paper, left=20mm, right=20mm, top=10mm}
\begin{document}
\chapter*{You exist, in my mind}
\begin{quote}
    \textit{I was 7, when my fear of the night first began.\\\\
        A child should sleep on their bed.\\\\
        Not under it.\\\\
        But just to make it clear, I wasn't scared of the night. In fact, I thrived during the darkest of hours and revelled when the midnight clock rang.
        I was scared of the night.
        No, not the night or the monsters that hid under my bed.
        No, not the night and all the dreary thoughts that would enter my head.
        Sleep.\\\\
        I was scared of sleep... absolutely terrified of it. I hated everything about it; from the false sense of security a dream gave you
        to the feeling of being ``alive'' a nightmare gave.
        I hated everything about it and all the lies about it, just the word itself was enough to throw of my whole mood.
        Thus, I can justify my hatred of sleep but not conclude it, I suppose it's been long enough for me to brush dust of old memories.
        Very well then, this is my story. Of a different world and a different time when the world was ghost-quite except for the crack of dawn and when problems
        started as quickly as they vanished.}
\end{quote}
\chapter{In this world, we have no one.}
18, June 1857
\paragraph{The grandfather clock rang.\\\\
    Rring Rring! Rring ring!
    Two giant arms and two steel fists were schedueled to arrive,
    began firing their empty rounds into empty space. Their rounds ricocheted of
    beaten-down walls and bounced around in my ears; rattling the ins and outs of
    my skull.\\\\
    Rring ring! Rring ring!
    Stacks of papers.\\\\
    Held down by the night candle and yet hovering over the table edge, began
rustling ruthlessly.}

\paragraph{The grandfather clock rang.\\\\
    Rring ring! Rring ring!\\\\
    Two giant arms and two heavy fists were cocked back like a revolver.
    Ready to fire their empty shells - into not-so-empty space.
    Their rounds ricocheted of bruised walls and bounced around my ears; rattling the ins and outs of my skull.\\\\
    Stacks of papers.\\\\
    Held down by the night candle and yet hovering over the table edge, rustled ruthlessly.\\\\
    Hair.\\\\
    Caged in knots and twists, swayed from side to side as the wind picked up its pace.\\\\
    Glass Bottles.\\\\
    Half full and half empty. Clanked as they rolled past each other; their insides swashing up and down like a ships rum on a stormy night.\\\\
    And a glass picture frame.
    My eyes were met with a loud thud.\\\\
    Then a gristly crunch.\\\\
    My eyes were fastened shut but I could still picture the wind sweeping away the crime scene; whistling as if nothing took place.
}
\end{document}

